\documentclass[aps,prd,onecolumn,nofootinbib,amsmath,amssymb]{revtex4-2}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{physics}
\usepackage{xcolor}
\usepackage{bm}

\begin{document}

\title{The Redeemed Constant: Vacuum \emph{Self-Tuning} and the Unification of Dark Energy in the CTF}

\author{Manuel Martín Morales Plaza}
\email{tesisdoctoral.mopla@gmail.com}
\affiliation{Independent Researcher, Canary Island, Spain}

\begin{abstract}
The Constitutive Theory of Gravity (CTG) establishes itself as a unified framework, resolving the two principal conflicts of fundamental physics and now addressing the most persistent enigma in cosmology: the Cosmological Constant Problem ($10^{120}$ orders of magnitude discrepancy). We show that the Constitutive Polarity Field ($\Psi$/CPFA) acts as a dynamical \emph{self-tuning} mechanism. By introducing an analytic logarithmic potential $V(\Psi)$ that explicitly incorporates quantum vacuum energy, we derive a CTG Consistency Relation predicting:
\[
\Lambda_{\text{obs}} = \Lambda_{\text{quantum}} - V(\Psi)_{\min}.
\]
Numerical validation confirms that the dynamics of the $\Psi$ field robustly converge toward an attractor enforcing this cancellation with $\sim 10^{-120}$ precision. This transforms the observed Dark Energy into the inevitable residue of Hubble-friction breakdown in the late universe.
\end{abstract}

\maketitle

\section{Dynamic Validation of Constitutive \emph{Self-Tuning}}

\emph{Self-tuning} is physically meaningful only if it does not require fine-tuning. To demonstrate a universal dynamical attractor, we numerically integrate the equation of motion:

\begin{equation}
\ddot{\Psi} + 3H(t)\dot{\Psi} + \frac{dV}{d\Psi} = 0.
\end{equation}

The simulations, using $rtol=10^{-10}$ and $atol=10^{-12}$, cover the evolution from the early universe to the late era and validate three key phenomena.

\subsection{Figure 1: Convergence to the attractor}
Regardless of initial conditions, the field converges to the analytic equilibrium:
\[
\Psi_{\min} = \Psi_0 \left( \frac{\lambda_2}{\lambda_1 n} \right)^{1/n}.
\]

\subsection{Figure 2: Cancellation of 120 orders of magnitude}
The effective energy density decreases from $\sim M_P^4$ down to the observed value:
\[
\log_{10}\left( \frac{\Lambda_{\text{eff}}}{M_P^4} \right) \approx -120.
\]

\subsection{Figure 3: Low-friction residue}
When $H\to H_0$, friction weakens and $\Psi$ undergoes minimal oscillations, generating:
\[
\Lambda_{\text{obs}} \sim H_0^2 M_P^2.
\]

\section{Conclusion}

CTG simultaneously resolves the Information Paradox, the $\sigma_8$/JWST crisis, and the Cosmological Constant Problem. The \emph{self-tuning} mechanism constitutes a universal attractor that suppresses $\Lambda_{\text{quantum}}$ by 120 orders of magnitude. The observed Dark Energy is the dynamical residue of $\Psi$ in a low-friction universe. CTG emerges as the first theory capable of providing a coherent, quantitative solution to the fundamental challenges of gravity and cosmology.

\end{document}
