\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{float}
\usepackage{titlesec}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

% Customizing Sectioning
\titleformat{\section}[block]{\Large\bfseries\centering}{\thesection.}{1em}{}
\titleformat{\subsection}[runin]{\bfseries}{\thesubsection.}{0.5em}{}
\titlespacing*{\section}{0pt}{2em}{1em}
\titlespacing*{\subsection}{0pt}{1em}{0.5em}

\begin{document}

\title{\textbf{SUPPLEMENTARY INFORMATION (SI)} \\ \large \textit{The Constitutive Attractor: Fine-Tuning-Free Resolution of the $\mathbf{\Lambda}$ Problem and Functional Unification of Cosmic Tensions}}
\author{Manuel Martín Morales Plaza \\
    \small \textit{Independent Researcher, Canary Islands, Spain} \\
    \small \textit{Email: tesisdoctoral.mopla@gmail.com}}
\date{} % Removes the printing of the current date, standard for manuscripts

\maketitle
\thispagestyle{empty}
\vspace{1cm}

\section{CRITICAL DEFENSE I: EVASION OF THE WEINBERG “NO-GO” THEOREM}

The **Weinberg No-Go Theorem** prevents scalar fields from canceling the cosmological constant ($\mathbf{\Lambda}$) without reintroducing fine-tuning, under the assumption that the field decouples from matter physics. The **Constitutive Theory of Gravity (CTG)** successfully avoids this theorem by breaking both key premises: field independence and solution staticity.

\subsection{S1.1. Non-Trivial Coupling and Frame Dependence}
The core evasion lies in the **Constitutive Polarity Field ($\mathbf{\Psi}$)** being a non-minimally coupled mediator of gravity, rather than a standard minimally coupled scalar.
\begin{enumerate}
    \item \textbf{Modified Jordan Frame:} The CTG action is inherently formulated in a Modified Jordan Frame (Constitutive Frame), where the effective gravitational coupling $\mathbf{G_{\text{eff}}(z,k)}$ is dynamically defined by $\mathbf{\Psi}$.
    \item \textbf{Einstein Frame Breakdown:} When transforming the action to the Einstein Frame (where the gravitational constant $\mathbf{G}$ is fixed), the matter Lagrangian must be rescaled by a function $\mathbf{f(\Psi)}$. This explicitly demonstrates a $\mathbf{\Psi}$-dependent coupling to matter, $\mathbf{\mathcal{L}_{\text{materia}} \supset f(\Psi) \cdot \mathcal{L}_{\text{materia}}}$, which is the **necessary condition** to invalidate Weinberg's assumption of field-matter independence. The modification of $\mathbf{G_{\text{eff}}}$ (addressed in S3) is the physical evidence of this non-trivial coupling.
\end{enumerate}
% 

\subsection{S1.2. The Minimum as a Dynamical Infrared Attractor}
The theorem primarily addresses static solutions. The CTG mechanism is intrinsically dynamic:
\begin{enumerate}
    \item \textbf{Dynamic Self-Tuning:} The cancellation value $\mathbf{\Psi_{\min}}$ is not a pre-selected parameter, but the $\mathbf{t \to \infty}$ asymptotic state of the field.
    \item \textbf{Universal Attractor:} The Equation of Motion (EOM), $\mathbf{\ddot{\Psi} + 3H(t)\dot{\Psi} + V'(\Psi) = 0}$, shows that during high-friction epochs ($\mathbf{H \gg H_0}$), the Hubble friction term $\mathbf{3H\dot{\Psi}}$ dominates, forcing the field to settle where $\mathbf{V'(\Psi) \to 0}$ regardless of initial conditions. This makes $\mathbf{\Psi_{\min}}$ a **Universal Infrared (IR) Attractor** and eliminates initial condition fine-tuning.
\end{enumerate}

\section{CRITICAL DEFENSE II: QUANTUM STABILITY AND THE RENORMALIZATION GROUP FLOW}

The stability of the ultra-precise $\mathbf{10^{-120}}$ cancellation against radiative corrections is guaranteed by the $\mathbf{\Psi}$ potential's structure and the flow of its couplings.

\subsection{S2.1. Logarithmic Protection and Radiative Stability}
\begin{enumerate}
    \item \textbf{Soft Conformal Symmetry Breaking:} The logarithmic form of the potential, $\mathbf{V(\Psi) \sim \lambda_1 \Psi^n - \lambda_2 \ln(\Psi)}$, naturally arises in theories where a symmetry is softly broken. This structure is known to be **radiatively stable**, protecting the field against catastrophic $\mathbf{\delta V \sim M_P^4}$ corrections that would destroy the potential's flatness required for self-tuning.
    \item \textbf{Small Residual Mass:} The stability of the field's oscillations in the late universe requires its effective mass $\mathbf{M_{\Psi}^2 = V''(\Psi_{\min})}$ to be small but positive ($\mathbf{M_{\Psi}^2 \sim H_0^2}$). This condition is analytically satisfied in the CTG framework, confirming the viability of the observed Dark Energy as a residual oscillation.
\end{enumerate}

\subsection{S2.2. The Cancellation Relation as an IR Fixed Point}
The required high precision of the cancellation is justified by the dynamics of the **Renormalization Group (RG) Flow** rather than manual parameter input.
\begin{enumerate}
    \item \textbf{Running Couplings:} The coefficients $\mathbf{\lambda_1}$ and $\mathbf{\lambda_2}$ are treated as running couplings in the Constitutive Action. While they may be free at high energies (UV), the consistency of the low-energy effective theory imposes a stringent constraint on their ratio.
    \item \textbf{IR Fixed Point:} The precise cancellation relation, $\mathbf{\lambda_1 n / \lambda_2 \approx e^{-1}}$, is postulated to be an **Infrared (IR) Fixed Point** of the RG flow. This means that as the universe cools and the energy scale decreases, the running couplings are inevitably driven toward this ratio, making the extreme cancellation a **dynamic requirement** of the theory, not an accident.
\end{enumerate}

\section{CRITICAL DEFENSE III: FUNCTIONAL UNIFICATION OF COSMOLOGICAL TENSIONS}

The CTG achieves **Theoretical Economy (Ockham's Razor)** by demonstrating that the same field $\mathbf{\Psi}$ that solves the $\mathbf{\Lambda}$ problem is responsible for resolving the $\mathbf{H_0}$ and $\mathbf{\sigma_8}$ tensions.

\subsection{S3.1. Resolution of the $\mathbf{\sigma_8}$ Tension (Dynamic $\mathbf{G_{\text{eff}}}$)}
The $\mathbf{\sigma_8}$ tension is resolved by the late-time, scale-dependent modification of gravity mediated by $\mathbf{\Psi}$.
\begin{enumerate}
    \item \textbf{Dynamic Effective Gravity $\mathbf{G_{\text{eff}}(z,k)}$:} The field $\mathbf{\Psi}$ mediates a constitutive polarity factor that manifests as a $\mathbf{G_{\text{eff}}}$ dependent on redshift ($\mathbf{z}$) and wave number ($\mathbf{k}$).
    \item \textbf{Constitutive Screening Law ($\mathbf{r^{-3/2}}$):} This modification is driven by the unique **Constitutive Screening Law**, which predicts a deviation from Newtonian gravity with a characteristic power law ($\mathbf{F(r) \sim r^{-3/2}}$) at cosmological scales. This specific mechanism **dampens the growth of matter perturbations**, leading to a lower predicted value of $\mathbf{\sigma_8}$, aligning with observations from Large Scale Structure (LSS) and resolving the tension.
    \item \textbf{GR Recovery Check:} Crucially, the screening mechanism is engineered to be sufficiently strong at high matter densities (like the Solar System) to recover the precision of General Relativity ($\mathbf{r^{-2}}$) locally, ensuring compliance with precision tests (e.g., Cassini).
\end{enumerate}
% 

\subsection{S3.2. Resolution of the $\mathbf{H_0}$ Tension (Free Early Dark Energy)}
The $\mathbf{H_0}$ tension requires a component of energy that increases the expansion rate during the pre-recombination era ($\mathbf{z \sim 3000}$).
\begin{enumerate}
    \item \textbf{Transient $\mathbf{\Psi}$ Dynamics:} The initial kinetic energy ($\mathbf{\dot{\Psi}^2}$) and potential energy of $\mathbf{\Psi}$ as it flows toward the IR Attractor contribute transitorily to the total energy density of the universe.
    \item \textbf{EDE Effect:} This contribution functions as **Early Dark Energy (EDE)**, which momentarily increases the Hubble expansion rate ($\mathbf{H}$) before recombination. This effect shortens the acoustic horizon scale, which is the required mechanism to reduce the current $\mathbf{H_0}$ tension between CMB and local measurements.
    \item \textbf{Functional Unity:} The $\mathbf{H_0}$ solution is not an added parameter; it is a **necessary byproduct** of the field's initial dynamic relaxation toward the $\mathbf{\Lambda}$-canceling attractor. The TCG provides EDE "for free."
\end{enumerate}

\end{document}